Particle rejuvenation of Rao-Blackwellized Sequential Monte Carlo smoothers for Conditionally Linear and Gaussian models

### 2017-07-03 TexArxiv/clgm.tex
Minor modifications for ArXiv

\includegraphics[scale=.3]{err_est}

@@

\includegraphics[scale=.3]{var2}

@@

Figure~\ref{fig:LogPriceTermStructure:data} compares the evolution of future $1M$ (the nearest contracts) to the \emph{term structure} observed from CME WTI crude oil, defined as the difference of future $13M$ and future $1M$ (to avoid seasonality). The figure shows that it is not necessary to have an inverse relationship between the  price of the nearest contract and the term structure. But when a significant drop in the price  of the nearest contract occurs, the term structure increases (i.e. in contango).
\begin{figure}
\centering
\includegraphics[scale=.6,angle=90]{LogPrice_TermStructure}
\caption{Log-price (red line) and slope of future curves (blue line).}
\label{fig:LogPriceTermStructure:data}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=.75,angle=90]{Posterior_Data}
	\caption{Posterior probability (triangle black) and slope of future curves (blue line).}
	\label{fig:posterior:data}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=.75]{Posterior_Data_LogPrice}
	\caption{Posterior probability (triangle black) and slope of future curves (blue line).}
	\label{fig:posterior:data:logprice}
\end{figure}

@@

\bibitem[BDM10]{briers:doucet:maskell:2010}
M.~Briers, A.~Doucet, and S.~Maskell.
\newblock Smoothing algorithms for state-space models.
\newblock {\em {A}nn. {I}nst. {S}tat. {M}ath}, 62(1):61--89, 2010.

\bibitem[BF63]{bryson:frazier:1963}
A.E. Bryson and M.~Frazier.
\newblock {Smoothing for linear and nonlinear dynamic systems}.
\newblock {\em {Proc. Optimum Sys. Synthesis Conf.}}, 1963.

@@

\bibitem[DLR77]{dempster:laird:rubin:1977}
A.~P. Dempster, N.~M. Laird, and D.~B. Rubin.
\newblock Maximum likelihood from incomplete data via the {EM} algorithm.
\newblock {\em Journal of the Royal Statistical Society B}, 39(1):1--38 (with
  discussion), 1977.

@@

\bibitem[FC03]{fearnhead:clifford:2003}
P.~Fearnhead and P.~Clifford.
\newblock {On-line inference for hidden {M}arkov models via particle filters}.
\newblock {\em {J.R. Statist. Soc. B}}, 65:887--899, 2003.

@@

\bibitem[HK98]{huerzeler:kunsch:1998}
M.~H{\"u}rzeler and H.~R. K{\"u}nsch.
\newblock {M}onte {C}arlo approximations for general state-space models.
\newblock {\em J. Comput. Graph. Statist.}, 7:175--193, 1998.

@@

\bibitem[Kal60]{kalman:1960}
R.E. Kalman.
\newblock {A new approach to linear filtering and prediction problems}.
\newblock {\em J. {B}asic {E}ngng}, 82:35--45, 1960.

>>>>

\includegraphics[scale=.3]{err_est.eps}

@@

\includegraphics[scale=.3]{var2.eps}

@@

Figure~\ref{fig:LogPriceTermStructure:data} compares the evolution of future $1M$ (the nearest contracts) to the \emph{term structure} observed from CME WTI crude oil, defined as the difference of future $13M$ and future $1M$ (to avoid seasonality). The figure shows that it is not necessary to have an inverse relationship between the  price of the nearest contract and the term structure. But when a significant drop in the price  of the nearest contract occurs, the term structure increases (i.e. in contango).
\begin{figure}
\centering
\includegraphics[scale=.6,angle=90]{LogPrice_TermStructure.eps}
\caption{Log-price (red line) and slope of future curves (blue line).}
\label{fig:LogPriceTermStructure:data}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=.75,angle=90]{Posterior_Data.eps}
	\caption{Posterior probability (triangle black) and slope of future curves (blue line).}
	\label{fig:posterior:data}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=.75]{Posterior_Data_LogPrice.eps}
	\caption{Posterior probability (triangle black) and slope of future curves (blue line).}
	\label{fig:posterior:data:logprice}
\end{figure}

@@

\bibitem[BDM10]{briers:doucet:maskell:2010}
M.~Briers, A.~Doucet, and S.~Maskell.
\newblock Smoothing algorithms for state-space models.
\newblock {\em {A}nnals of the {I}nstitute of {S}tatistical {M}athematics}, 62(1):61--89, 2010.

\bibitem[BF63]{bryson:frazier:1963}
A.E. Bryson and M.~Frazier.
\newblock {Smoothing for linear and nonlinear dynamic systems}.
\newblock {\em {Proceedings of the optimum system synthesis conference}}, 1963.

@@

\bibitem[DLR77]{dempster:laird:rubin:1977}
A.~P. Dempster, N.~M. Laird, and D.~B. Rubin.
\newblock Maximum likelihood from incomplete data via the {EM} algorithm.
\newblock {\em Journal of the Royal Statistical Society: Series B}, 39(1):1--38 (with
  discussion), 1977.

@@

\bibitem[FC03]{fearnhead:clifford:2003}
P.~Fearnhead and P.~Clifford.
\newblock {On-line inference for hidden {M}arkov models via particle filters}.
\newblock {\em {Journal of the Royal Statistical Society: Series B}}, 65:887--899, 2003.

@@

\bibitem[HK98]{huerzeler:kunsch:1998}
M.~H{\"u}rzeler and H.~R. K{\"u}nsch.
\newblock {M}onte {C}arlo approximations for general state-space models.
\newblock {\em Journal of {C}omputational and {G}raphical {S}tatistics}, 7:175--193, 1998.

@@

\bibitem[Kal60]{kalman:1960}
R.E. Kalman.
\newblock {A new approach to linear filtering and prediction problems}.
\newblock {\em Journal of {B}asic {E}ngineering}, 82:35--45, 1960.
